---
title: "partner_a_task"
format: html
editor: visual
---

# Documenting nanoplot

## Step 1:

```{bash}
#| eval: false
conda create --name partner_b_nanoplot -y  # -y means "yes" to all questions automatically
```

## Step 2:

```{bash}
#| eval: false
conda activate partner_b_nanoplot
```

## Step 3:

```{bash}
#| eval: false
conda install -c bioconda nanoplot -y
```

## Step 4:

```{bash}
#| eval: false
mkdir envs
```

## Step 5:

```{bash}
#| eval: false
# Example export command:
conda env export --from-history > envs/partner_b_nanoplot.yml
```

# Importing env

## Step 1:

```{bash}
#| eval: false
conda env create -f envs/partner_b_nanoplot.yml -n partner_b_nanoplot
conda activate partner_b_nanoplot
NanoPlot --help
```

# Docker

```{bash}
#| eval: false
docker pull staphb/quast:5.3.0 --platform linux/amd64
docker run -v -it taphb/quast:5.3.0 --help

```

## **why do we use staphb/quast**

staphb/quast is used to evaluate and compare genome assemblies

```{r}
library("tidyverse")
yeast_genome <- read_csv("yeast_genome_metadata.csv") %>% #reading the .csv file
  filter (genome_size_mb > 12) %>% #removing all the data points less than 12
  mutate(log_depth = log(sequencing_depth)) %>% # creating a new qualum whre I will save all the value sequencing_depth after taking the log
  select (gc_content, genome_size_mb, sequencing_depth) %>% #selecting the columns which we need
  write_csv("partner_a_filtered.csv") #savig the csv file

yeast_genome_matrix <- as.matrix(yeast_genome) # cnverting the dataset to matrix form

write.csv(yeast_genome_matrix, "partner_a_matrix.csv") # save as csv

mean_gc_content <- mean(yeast_genome_matrix[,"gc_content"]) # taking mean
mean_gc_content
```

```{r}
ggplot(data = yeast_genome_matrix, aes(x = genome_size_mb, y = sequencing_depth)) +
  geom_point() +
  labs(title = "scatter plot", x = "genome_size_mb", y = "sequencing_depth") +
  theme_minimal() #plotting the scatterplot

```

## Filtlong Setup Documentation - B1

Step 1: Searching for filtlong

```{bash}
#| eval: false
conda search -c bioconda filtlong 
```

Step 2: Create the environment

```{bash}
#| eval: false
conda create --name partner_b_filtlong -y  
```

Step 3: Activate environment

```{bash}
#| eval: false
conda activate partner_b_filtlong 
```

Step 4: Install Filtlong into environment

```{bash}
#| eval: false
conda install -c bioconda filtlong -y
```

Step 4: Export into a yml file in an "envs" environment

```{bash}
#| eval: false
conda env export --from-history > envs/partner_b_filtlong.yml
```

Step 5: Commit and push, proceed to import partner A's Tools

```{bash}
#| eval: false
conda activate partner_a_nanoplot
NanoPlot --help
```

## Setting up Docker - B1

#### Dorado is a high-performance, open-source command-line basecaller developed by **Oxford Nanopore Technologies** (ONT) to convert raw electrical signals (POD5/Fast5) into DNA/RNA sequences.

Step 1: Pull Docker

```{bash}
#| eval: false
# In the terminal 
docker pull --platform linux/amd64 nanoporetech/dorado:latest
## Platform used: 
docker run --rm --platform linux/amd64 -it nanoporetech/dorado:latest --help
```

Step 2: Run Docker

```{bash}
#| eval: false
docker run --rm -it nanoporetech/dorado:latest dorado --help
```

## **The R Data Challenge (Wrangling & Visualization) - B1**

```{r}
yeast_dataframe <- read_csv("yeast_genome_metadata.csv") %>%
  filter (gc_content < 40) %>%
  mutate(quality_status = if_else (
    sequencing_depth > 50, "High", "Low"
  )) 
high_quality_samples <- filter (yeast_dataframe, quality_status == "High") %>% select(sample_id)

high_quality_samples_vec <- high_quality_samples$sample_id
write_csv(yeast_dataframe, "partner_b1_filtered.csv")

ggplot (yeast_dataframe, aes(x= sequencing_depth)) +
  geom_histogram (aes(color= quality_status, fill= quality_status)) +
  ggtitle("Sequencing Depth Vs. Quality Status") +
  theme_minimal()
```

## Filtlong setup

Step 1: create environment

```{bash}
#| eval: false
conda create --name partner_Krish(B1)_filtlong -y
```

Step 2: activate environment

```{bash}
#| eval: false
conda activate partner_Krish(B1)_filtlong
```

Step 3: install filtlong

```{bash}
#| eval: false
onda install -c bioconda filtlong
```

## Docker setup and Dorado info

Dorado is a high-performance, open-source command-line basecaller developed by **Oxford Nanopore Technologies** (ONT) to convert raw electrical signals (POD5/Fast5) into DNA/RNA sequences.

```{bash}
#| eval: false
#open the docker app on the desktop
#open the terminal
docker pull --platform linux/amd64 nanoporetech/dorado:latest
docker run --rm --platform linux/amd64 -it nanoporetech/dorado:latest --help
```

## Tidyverse setup

```{r}
#| eco: "false"
library("tidyverse")
```

```{r}
yeast_mata_data <- read.csv("yeast_genome_metadata.csv")
yeast_mata_data_filtered <- yeast_mata_data%>%
  filter(gc_content < 40)%>% 
  mutate(quality_status = if_else(sequencing_depth > 50, "High", "Low"))

high_quality_samples <- yeast_mata_data_filtered%>%
  filter(quality_status == "High") %>% select(sample_id)

high_quality_samples_vector <- high_quality_samples$sample_id
write_csv(yeast_mata_data_filtered, "partner_Krish(B2)_filtered.csv")

```

```{r}
ggplot(data = yeast_mata_data_filtered, aes(x = sequencing_depth)) +
  geom_histogram() +
  labs(title = "Yeast_meta_data", x = "sequencing_depth") +
  theme_minimal()
```
