---
title: "reproducible_workflow"
author: "Kimia Mansouri(B1)"
format: html
editor: visual
toc : true
---

```{r}
#| eval: false 
#| echo: false
library ("tidyverse")
```

## Filtlong Setup Documentation - B1

Step 1: Searching for filtlong

```{bash}
#| eval: false
conda search -c bioconda filtlong 
```

Step 2: Create the environment

```{bash}
#| eval: false
conda create --name partner_b_filtlong -y  
```

Step 3: Activate environment

```{bash}
#| eval: false
conda activate partner_b_filtlong 
```

Step 4: Install Filtlong into environment

```{bash}
#| eval: false
conda install -c bioconda filtlong -y
```

Step 4: Export into a yml file in an "envs" environment

```{bash}
#| eval: false
conda env export --from-history > envs/partner_b_filtlong.yml
```

Step 5: Commit and push, proceed to import partner A's Tools

```{bash}
#| eval: false
conda activate partner_a_nanoplot
NanoPlot --help
```

## Setting up Docker - B1

#### Dorado is a high-performance, open-source command-line basecaller developed by **Oxford Nanopore Technologies** (ONT) to convert raw electrical signals (POD5/Fast5) into DNA/RNA sequences.

Step 1: Pull Docker

```{bash}
#| eval: false
# In the terminal 
docker pull --platform linux/amd64 nanoporetech/dorado:latest
## Platform used: 
docker run --rm --platform linux/amd64 -it nanoporetech/dorado:latest --help
```

Step 2: Run Docker

```{bash}
#| eval: false
docker run --rm -it nanoporetech/dorado:latest dorado --help
```

## **The R Data Challenge (Wrangling & Visualization)**

```{r}
yeast_dataframe <- read_csv("yeast_genome_metadata.csv") %>%
  filter (gc_content < 40) %>%
  mutate(quality_status = if_else (
    sequencing_depth > 50, "High", "Low"
  )) 
high_quality_samples <- filter (yeast_dataframe, quality_status == "High") %>% select(sample_id)

high_quality_samples_vec <- high_quality_samples$sample_id
write_csv(yeast_dataframe, "partner_b1_filtered.csv")

ggplot (yeast_dataframe, aes(x= sequencing_depth)) +
  geom_histogram (aes(color= quality_status, fill= quality_status)) +
  ggtitle("Sequencing Depth Vs. Quality Status") +
  theme_minimal()
```
